XS-Face: Merge Raw Data

### 2020-08-14 analysis/1_merge_data/merge_all_data.Rmd
add cropping by fisheye to preprocessing, redo paths

## Step 1: Load detectors
### Load detectors from MTCNN
```{r}
dets_MTCNN <- read_csv("../../data/final_detector_output/mtcnn3.csv") %>%
  mutate(subid = video) %>%
  mutate(frame = as.numeric(frame)) %>%
  mutate(faceMT = as.logical(is_face)) %>%
  distinct(video,frame,.keep_all=TRUE)   
```

@@

### Load OpenPose detections (face and wrists)
Wrists: if right or left wrist was ever detected
Faces: If nose was ever detected

```{r}
detsOpenPose <- read_csv("../../data/final_detector_output/openpose_results_truncated_2.csv") 
detsOpenPose <- detsOpenPose %>%
  mutate(video = name) %>%
  distinct(video,frame,.keep_all=TRUE)  %>%
  mutate(frame = as.numeric(frame) + 1) %>% ## Frame output is off by one since we extracted from videos vs. frames.
  mutate(faceOP = Nose_conf!=0)  %>%  
  mutate(wristOP = LWrist_conf!=0 | RWrist_conf!=0 )   %>%
  mutate(faceOPStrict = Nose_conf>.5)  %>%  
  mutate(wristOPStrict = LWrist_conf>.5 | RWrist_conf>.5 )   
```

## Step 2:  Merge detectors and sanity check
```{r}
assert_that(dim(dets_MTCNN)[1]==dim(detsViola)[1]) 
alldets=left_join(dets_MTCNN,detsViola[,c("video","frame","faceVJ")])  ## Join MTCNN + Viola Jones
alldets=left_join(alldets,detsOpenPose[,c("video","frame","faceOP","wristOP", "faceOPStrict", "wristOPStrict")])  ##  ++ OpenPose
```

@@

### Merge in frame times, postures, and orientations
```{r}
# calls helper functions in helper.r to get times and posture coding integrated
d <- alldets %>%
  select(-c(is_face,video)) %>% # redudant with faceMT & subid, dropping
  left_join(demo.data) %>% # join demographics info 
  group_by(subid) %>% # get subid
  do(add.times(.)) %>%  # calls helper functions to add times
  group_by(subid) %>%
  do(add.posture(.)) %>% ## adds both postures and orientatinos
  do(add.posture.second(.)) ## gets reliability coding for postures
```

@@

# Step 4: Save out the data
```{r}
write_csv(d, "../data/consolidated_data/consolidated_data_4detectors_july2020.csv") #
```

>>>>

## Step 1: Load detectors

### Load demographics
```{r}
# All of the videos were filmed with an MD-80 headcam. Some videos had a fisheye lens attached to them that increased their FOV by approximately 50% in both directions (see manuscript; in demographics column "fisheye"). This was determined by looking at the third-person videos.

# The original resolutoin fo ALL of the videos is 480 x 720. But, then, OpenPose resizes them (not sure why?) and adds some blank space so that it is the right space -- this blank space is on the RIGHT. The final resolution becomes 1280 x 720; all vertical space has meaningful detections, but all horizontal space does not

# In order to make the detections comparable, we need to restrict detections to center FOV for fisheye participants.
### Specify cropping for participants with fish-eye lens

## pop out fisheye versus none
demo <- read.csv(paste0(here::here(),"/data/demographics/demographics_updated.csv"))

fisheye_subs <- demo %>%
  filter(Fisheye=='yes')

no_fisheye_subs <- demo %>%
  filter(Fisheye=='no')

# based on difference in view angle between veho/muvi-80
vertical_diff = (1 - (47/64))/2
horizontal_diff = (1 - (36/46))/2

# vid params
# x_max = 1280 # actual max -- black space between 1080 and 1280
x_max = 1080 # max with content
y_max = 720

# cropping params -- c
limit_lower_y = vertical_diff*y_max
limit_upper_y = (1 - vertical_diff)*y_max

limit_lower_x = horizontal_diff*x_max
limit_upper_x = (1 - horizontal_diff)*x_max

### Load detectors from MTCNN
```{r}
dets_MTCNN <- read_csv("../../data/final_detector_output/mtcnn3.csv") %>%
  mutate(subid = video) %>%
  mutate(frame = as.numeric(frame)) %>%
  mutate(faceMT = as.logical(is_face)) %>%
  distinct(video,frame,.keep_all=TRUE)   
```

@@

### Load & Preprocess OpenPose detections (face and wrists)
Wrists: if right or left wrist was ever detected
Faces: If nose was ever detected

```{r}
detsOpenPoseRaw <- read_csv(paste0(here::here(),"/data/final_detector_output/openpose_results_truncated_2.csv")) %>%
  mutate(subid = name, video = name) %>%
  distinct(subid,frame,.keep_all=TRUE) %>%
  mutate(frame = as.numeric(frame) + 1)  ## Frame output is off by one since we extracted from videos vs. frames.
```

## break out detetions for fisheye vs non
```{r}
# dets for subs w/o fisheye lens 
detsOpenPose_no_fisheye <- no_fisheye_subs %>%
  left_join(detsOpenPoseRaw) %>%
  mutate(faceOP = Nose_conf!=0)  %>%  
  mutate(wristOP = LWrist_conf!=0 | RWrist_conf!=0 )   %>%
  mutate(faceOPStrict = Nose_conf>.5)  %>%  
  mutate(wristOPStrict = LWrist_conf>.5 | RWrist_conf>.5 )   %>%
  mutate(faceOPAll = faceOP,wristOPAll = wristOP, faceOPStrictAll = faceOPStrict, wristOPStrictAll = wristOPStrict)

# dets for subs w fisheye lens 
detsOpenPose_fisheye <- fisheye_subs %>%
  left_join(detsOpenPoseRaw) %>%
  mutate(faceOPAll = Nose_conf!=0)  %>%  
  mutate(wristOPAll = LWrist_conf!=0 | RWrist_conf!=0 )   %>%
  mutate(faceOPStrictAll = Nose_conf>.5)  %>%  
  mutate(wristOPStrictAll = LWrist_conf>.5 | RWrist_conf>.5 ) %>%
  mutate(noseOP_center = (Nose_y<(limit_upper_y) & Nose_x<(limit_upper_x) & Nose_y>(limit_lower_y) & Nose_x>(limit_lower_x))) %>%
  mutate(wristOPLeft_center = (LWrist_y<(limit_upper_y) & LWrist_x<(limit_upper_x) & LWrist_y>(limit_lower_y) & LWrist_x>(limit_lower_x)))  %>%
  mutate(wristOPRight_center = (RWrist_y<(limit_upper_y) & RWrist_x<(limit_upper_x) & RWrist_y>(limit_lower_y) & RWrist_x>(limit_lower_x)))  %>%
  mutate(faceOP = Nose_conf!=0 & noseOP_center) %>%  
  mutate(wristOP = (LWrist_conf!=0 & wristOPLeft_center) | (wristOPRight_center & RWrist_conf!=0 )) %>%
  mutate(faceOPStrict = Nose_conf>.5 & noseOP_center) %>%  
  mutate(wristOPStrict = (LWrist_conf>.5 & wristOPLeft_center) | (wristOPRight_center & RWrist_conf>.5 )) %>%
  select(-noseOP_center, -wristOPLeft_center, -wristOPRight_center)

detsOpenPose <- detsOpenPose_no_fisheye %>%
  full_join(detsOpenPose_fisheye)
```

## Step 2:  Merge detectors and sanity check
```{r}
assert_that(dim(dets_MTCNN)[1]==dim(detsViola)[1]) 
alldets=left_join(dets_MTCNN,detsViola[,c("video","frame","faceVJ")])  ## Join MTCNN + Viola Jones

alldets=left_join(alldets,detsOpenPose[,c("video","frame","faceOP","wristOP", "faceOPStrict", "wristOPStrict", "faceOPAll","wristOPAll", "faceOPStrictAll", "wristOPStrictAll")])  ##  ++ OpenPose
```

@@

### Merge in frame times, postures, and orientations
```{r}
# calls helper functions in helper.r to get times and posture coding integrated
d <- alldets %>%
  select(-c(is_face,video)) %>% # redudant with faceMT & subid, dropping
  left_join(demo.data) %>% # join demographics info 
  group_by(subid) %>% # get subid
  do(add.times(.)) %>%  # calls helper functions to add times
  group_by(subid) %>%
  do(add.posture(.)) 
```

@@

# Step 4: Save out the data
```{r}
write_csv(d, paste0(here::here(), "/data/consolidated_data/consolidated_data_4detectors_aug2020.csv")) 
```
